Equalizer 2\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Minor tweaks
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@50 db7c848b-7755-4df2-b763-8796797afa52

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Equalizer 2.0\\Convergence of a Parallel Rendering Framework}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
  \begin{abstract}
    Developing complex, real world graphics applications which utilize multiple GPUs and
    computers for interactive 3D rendering tasks can be a daunting task, in
    particular since it requires expertise in distributed systems and parallel
    rendering in addition to the application domain itself. We present a mature
    parallel rendering framework which provides a large set of features,
    algorithms and system integration for a wide range of real-world research
    and industry applications. Based on the basic architecture and
    implementation of the \textsf{Equalizer} parallel rendering framework presented in
    \cite{EMP:09}, we show how a variety of generic algorithms are integrated in the
    framework to help application development in many different domains, and we show
    a number of applications highlighting the diverse aspects and use cases of \textsf{Equalizer}.
  \end{abstract}

@@

%----------------------------------------------------------------------
\begin{figure*}[ht]\center
  \includegraphics[width=2\columnwidth]{images/teaser} \\
  (a) \hfil \hfil (b) \hfil \hfil (c)
  \vspace{-2mm}
  \caption{Example \textsf{Equalizer} application use cases: (a) 192 Megapixel CAVE at
    KAUST running RTNeuron, (b) Immersive HMD with external tracked and
    untracked views running RTT DeltaGen for virtual car usability studies, and (c)
    Cave2 running a molecular visualization build based on Omegalib.}
  \label{FIG_teaser}
\end{figure*}

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Equalizer 2\\Convergence of a Parallel Rendering Framework}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
  \begin{abstract}
    Developing complex, real world graphics applications which utilize multiple
    GPUs and computers for interactive 3D rendering tasks is a complex task, it
    requires expertise in distributed systems and parallel rendering in addition
    to the application domain itself. We present a mature parallel rendering
    framework which provides a large set of features, algorithms and system
    integration for a wide range of real-world research and industry
    applications. Based on the basic architecture and implementation of the
    \textsf{Equalizer} parallel rendering framework presented in \cite{EMP:09},
    we show how a variety of generic algorithms are integrated in the framework
    to help application scalability and development in many different domains,
    highlight how concrete applications benefit from the diverse aspects and use
    cases of \textsf{Equalizer}, and show new experimental results for parallel
    rendering and data distribution.
  \end{abstract}

@@

%----------------------------------------------------------------------
\begin{figure*}[ht]\center
  \includegraphics[width=2\columnwidth]{images/teaser} \\
  (a) \hfil \hfil (b) \hfil \hfil (c)
  \vspace{-2mm}
  \caption{Example Equalizer applications: (a) 192 Megapixel CAVE at
    KAUST running RTNeuron, (b) Immersive HMD with external tracked and
    untracked views running RTT DeltaGen for virtual car usability studies,
    and (c) Cave2 running a molecular visualization.}
  \label{FIG_teaser}
\end{figure*}
